Response to the defense feedback

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}
\section{Side-channels}
A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information. In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}. He demonstrated that an attacker could break cryptosystems such as RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. As a result, an attacker can infer the whole secret key by measuring the execution time of the operation. Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+,7163050}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present the related work of the dissertation in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations and future work.

>>>>

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software was done with around 100,000 lines of code. 
Today, a mobile application such as Telegram contains more than 2,000,000 lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code.

\section{Side-channels}
A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information. In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}. He demonstrated that an attacker could break cryptosystems such as RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. As a result, an attacker can infer the whole secret key by measuring the execution time of the operation. Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+,7163050}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present the related work of the dissertation in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations and future work of the dissertation research.
